

# Filtering Orgs

First reading in our data from our preprocessing steps:

```{r}
library(tidyverse)
#library(sf)
org_data <- read_rds(here::here("data", "processed", "org_data.rds"))

```

# Filter out foundation code 00 orgs

Based on https://www.irs.gov/pub/irs-soi/eo-info.pdf 
page 3 - we will exclude 00 for foundation code - all orgs except 501c3 to filter down to 501c3 - looks like they are coded as 0 instead of 00.

We start with `r nrow(org_data)` rows.
```{r}
found_00_orgs <- org_data %>% filter(BMF_FOUNDATION_CODE == "0")  %>% dplyr::select(ORG_NAME_CURRENT) 

found_00_orgs %>% head( n = 10) #show a couple of examples of what will be dropped

org_data <- org_data %>% filter(is.na(BMF_FOUNDATION_CODE)| BMF_FOUNDATION_CODE != "0")# keeping NA values
```

After filtering out these orgs, we end with `r nrow(org_data)` rows, removing `r nrow(found_00_orgs)` orgs with foundation code 00.


# Filter out social_clubs 

We start with `r nrow(org_data)` rows.

See page 16 for more information: https://nccs.urban.org/pubs/nccs-data-guide.pdf and see https://urbaninstitute.github.io/nccs-legacy/ntee/ntee-history.html. 

```{r}
socialclubs <-org_data %>% filter(str_starts(string = NTEE_IRS, pattern = "Y|y"))
socialclubs %>% dplyr::select(ORG_NAME_CURRENT)

org_data <- org_data %>% filter(!str_starts(string = NTEE_IRS, pattern = "Y|y")| is.na(NTEE_IRS)) # keeping NA values
```


After filtering out social clubs we end up with `r nrow(org_data)` rows, removing `r nrow(socialclubs)` social club orgs.

# Filter out PO Boxes

```{r}
Post_offices <- org_data %>% filter(str_detect(F990_ORG_ADDR_STREET, "BOX|POST OFFICE"))
Post_offices_Box <- Post_offices  %>% filter(!str_detect(F990_ORG_ADDR_STREET, "PO"))# let's check the more unusal addresses
Post_offices_Box$F990_ORG_ADDR_STREET

# based on Gemina 1.5 Pro AI search on aug20 2026 the following are likely physical addresses and not just mail boxes
#2901 DRUID PARK DRIVE P O BOX 40
#1 E CHASE ST STE R3G MAIL BOX 9
#900 CATON AVENUE BOX 123


```

Preserving addresses that look like post office boxes but are physical: 
```{r}
Post_offices <- org_data %>% filter(str_detect(F990_ORG_ADDR_STREET, "822 GUILFORD AVE BOX 235|3717 BOSTON STREET BOX 345|MAIL BOX|P O BOX|PO BOX|POST OFFICE"))

org_data <- org_data %>% filter(!str_detect(F990_ORG_ADDR_STREET, "822 GUILFORD AVE BOX 235|3717 BOSTON STREET BOX 345|MAIL BOX|P O BOX|PO BOX|POST OFFICE")| is.na(F990_ORG_ADDR_STREET)) # keeping NA values)
```

After filtering out PO Boxes we end up with `r nrow(org_data)` rows, removing `r nrow(Post_offices)`  orgs with a post office box address.

# Filter out foundation code 04 and 17


- 04 = Private non-operating foundation
- 17 = Organizations operated solely for the benefit of and in conjunction with organizations with code 10 through 16 

We want to remove these and set them aside. 

Let's keep on their own as an aside but remove from main data.

```{r}
no_oper_orgs<-org_data %>% filter(BMF_FOUNDATION_CODE %in% c("4","17"))  %>% dplyr::select(ORG_NAME_CURRENT)  #show examples of what will be dropped
no_oper_orgs %>% head( n = 10)

org_data <- org_data %>% filter(is.na(BMF_FOUNDATION_CODE)| ! BMF_FOUNDATION_CODE  %in% c("4","17"))# keeping NA values

```

After filtering out these orgs we end up with `r nrow(org_data)` rows, removing `r nrow(no_oper_orgs)` orgs with foundation code 04 or 17. 

# Filtering for year

Filing is due May 15 each year, since the data is from March 2024, that means it only shows 2023 complete data.

Orgs only need to file every 3 years as well, but this would be a sliding window for orgs at different times as, but we could require that the last filing time be within the last 3 complete years.

According to the [dictionary](https://nccsdata.s3.amazonaws.com/harmonized/harmonized_data_dictionary.xlsx):

- ORG_FISCAL_YEAR	= Fiscal Year of the BMF from which this record was pulled
- ORG_YEAR_LAST =	Most recent year EIN was recorded in BMF



If we assume a sliding window and people would need to have filed in the last 3 complete years, than we can include orgs that filed in 2021, 2022, and 2023 (as well as the incomplete 2024).


```{r}
active_orgs <- org_data %>% filter(ORG_YEAR_LAST %in% c(2024, 2023, 2022, 2021))
non_active_orgs <- org_data %>% filter(! ORG_YEAR_LAST %in% c(2024, 2023, 2022, 2021)| is.na(ORG_YEAR_LAST))

count(active_orgs, ORG_YEAR_LAST)
```

Filtering from the total `r nrow(org_data)` orgs, we have  `r nrow(active_orgs)` active orgs, removing `r nrow(non_active_orgs)` orgs with thatlast filed before 2021.


Now let's remove orgs from industrial neighborhoods with Population of 0 or NA.

Let's first check what those neighborhoods are.


```{r}
active_orgs %>% filter(is.na(Population)) # this is two orgs in a park
popzero <-active_orgs %>% filter(Population== 0) 
popzero %>% dplyr::select(Name) # do these make sense?

popmissing <- active_orgs %>% filter(is.na(Population))
popmissing %>% count(Population)
popzero %>% count(Population)
```

OK these make sense. Let's remove them.

```{r}

#first nrow before removal
nrow(active_orgs)
active_orgs <-active_orgs %>% filter(Population!= 0) %>% filter(!is.na(Population))
nrow(active_orgs)
nrow(popzero)
# OK this looks right

```


Let's save our files.

```{r}
write_rds(active_orgs, file = here::here("data", "processed", "active_orgs.rds"))
write_csv(non_active_orgs, file = here::here("data", "processed", "non_active_orgs.csv"))
```
