---
title: "Baltimore Nonprofit Analysis"
output:
  pdf_document:
    toc: yes
  html_document:
    self_contained: yes
    code_download: yes
    highlight: tango
    number_sections: no
    theme: cosmo
    toc: yes
    toc_float: yes
  word_document:
    toc: yes
---


```{r, message= FALSE}
library(readxl)
library(here)
library(tidyverse)
library(stringr)
library(naniar)
```

## Import data
```{r}
df_simplified<-read_excel(here::here("Nonprofit_Baltimore_Analysis.xlsx"), sheet = 3)
```

Information about the data: 
Here’s an [article](https://nccs.urban.org/sites/default/files/2018-12/Guide%20to%20Using%20NCCS%20Data.pdf) describing some of the datasets from the IRS 990s.  
We’re using the BMF.  There’s a section titled “Minimum Filing Threshold” that explains a data limitation (and why we’re seeing so many 0’s).

It seems that if there is a value less than 50,000 other than zero, it must mean that the organization decided to submit to the IRS, because otherwise they would be listed as a zero. It is not possible to distinguish a true zero from a zero due to not meeting the threshold of 50,000 and just not submitting.

It therefore makes sense to remove zero values and to report this caveat that the data is incomplete because many nonprofits that had assets less than 50,000 are not included.

However for the high vs nonhigh asset we could keep these - because zero values would still be less than the threshold regardless.

Adding to this NA values can be considered less than 50000, as organizations are not required to report an amount if they have less than 50000.

## Tidying data

### Asset amount

First want to recode our data based on Asset amounts. We will check if there are `NA` values for asset amounts.

```{r}
gg_miss_var(df_simplified)
```

Yes, indeed there are...
Thus, we will recode asset amount based on a threshold of greater than or equal to 50,000 as high asset and less than 50000 as not high asset.

```{r}

df_simplified<-df_simplified %>%
  # modify Asset amount variable to be numeric
  mutate(ASSET_AMT =as.numeric(ASSET_AMT)) %>%
  #create a variable about high asset amount (threshold being $500,000)
  mutate(ASSET_High = case_when(ASSET_AMT >= 500000 ~ TRUE,
                                ASSET_AMT  < 500000 ~ FALSE))
```

Here we can see the NA values:

```{r}
table(df_simplified$ASSET_High, useNA = "always")
```

Now we will replace `NA` values with `False` as well:

```{r}
 df_simplified <- df_simplified %>%  
  mutate(ASSET_High = replace_na(ASSET_High, FALSE)) #NA values will be coded as not high asset (if no cases match the other two ASSET_AMT statements then code as FALSE) based on the above logic
```

Check that this worked and that there are no NA values now:

```{r}
table(df_simplified$ASSET_High, useNA = "always")
```

Now we will convert these to text as another variable and also create a log version of the asset amount.

```{r}
 df_simplified<-df_simplified %>%
  mutate(ASSET_High_text = case_when(ASSET_High  == TRUE ~ "High Asset",
                                     ASSET_High  == FALSE ~ "Low Asset")) %>%
  # we will also create new log of asset amount variable
  mutate(ASSET_AMT_log = log(ASSET_AMT))
```

### Neighborhood category

Next we will modify the data to include a variable about the percentage of African American/Black people.
```{r}
  # create new Percent_AA variable by converting `Normalized African American Population` variable into a percentage and rounding
 df_simplified<-df_simplified %>%
  mutate(Percent_AA = 
           round(`Normalized African American Population`*100, digits = 1))  %>%

  # create new Majority_AA variable that indicates if Percent_AA is greater than or equal to 50% or not
  mutate(Majority_AA = case_when(
    Percent_AA >= 50 ~ "Yes", 
    Percent_AA <  50 ~ "No")) %>%
  # create a new variable about this in text
   mutate(Neighborhood = case_when(
    Percent_AA >= 50 ~ "Majority\nBlack", 
    Percent_AA <  50 ~ "Majority\nNon-Black")) %>% 
  # make this a factor and order by level appearance in the data
  mutate(Neighborhood = as_factor(Neighborhood),
         Neighborhood = forcats::fct_inorder(Neighborhood))
```

### Quantile data
To group the data by quantiles, we first remove organizations with zero assets because we don't know if zero values are real. If assets are under 50,000, organizations can report as zero also.

Similarly, NA values could be anything between 0 and less than 50,000. Thus we aren't sure what those asset amounts are.
```{r}
 # make a new dataframe without zeros and NA asset amounts
df_simplified_no_zero<-df_simplified %>%
    drop_na(ASSET_AMT) %>% #redundant with the next line but shows we are dropping NA values
    filter(ASSET_AMT>0) %>% # ASSET_AMT must be greater than zero
  # get quartiles
    mutate(ASSET_quartile = ntile(ASSET_AMT, 4)) %>%
  # create new quartile variable that specifies quartiles by text
    mutate(ASSET_quartile_text = case_when(ASSET_quartile == 1 ~ "1st_Quartile",
                                           ASSET_quartile == 2 ~ "2nd_Quartile",
                                           ASSET_quartile == 3 ~ "3rd_Quartile",
                                           ASSET_quartile == 4 ~ "4th_Quartile"))

#Now check:
table(df_simplified_no_zero$ASSET_quartile, useNA = "always")

df_simplified_no_zero%>% group_by(ASSET_quartile_text) %>% summarise(range = range(ASSET_AMT))

```


Without removal (except NAs)- since these asset amounts might night influence quartiles. 
```{r}

df_simplified_no_removal<-df_simplified %>%
    drop_na(ASSET_AMT) %>% #dropping NA values
  # get quartiles
    mutate(ASSET_quartile = ntile(ASSET_AMT, 4)) %>%
  # create new quartile variable that specifies quartiles by text
    mutate(ASSET_quartile_text = case_when(ASSET_quartile == 1 ~ "1st_Quartile",
                                           ASSET_quartile == 2 ~ "2nd_Quartile",
                                           ASSET_quartile == 3 ~ "3rd_Quartile",
                                           ASSET_quartile == 4 ~ "4th_Quartile"))

#Now check:
table(df_simplified_no_removal$ASSET_quartile, useNA = "always")

df_simplified_no_removal %>% group_by(ASSET_quartile_text) %>% summarise(range = range(ASSET_AMT))
```

Turns out this doesn't really work because the 1st and 2nd quartiles can't be distinguished as we don't know if the values of 0 are actually some number below 50,000 and both quartlies have a max of less than 50,000. So we will stick with our removal.

## NTEE recoding

```{r}
df_simplified <-df_simplified %>%
  mutate(NTEE_text = case_when(
    str_starts(NTEE_CD, pattern = "A")~ "Arts", # if NTEE_CD starts with A make new variable value "Arts" etc.
    str_starts(NTEE_CD, pattern = "B") ~ "Education",
    str_starts(NTEE_CD, pattern = "C|D") ~ "Environment/Animals", # if NTEE_CD value starts with C or D make new variable value "Environment/Animals"
    str_starts(NTEE_CD, pattern = "E|F|G|H") ~ "Health",
    str_starts(NTEE_CD, pattern = "I|J|K|L|M|N|O|P") ~ "Human Services",
    str_starts(NTEE_CD, pattern = "Q") ~ "International Affairs",
    str_starts(NTEE_CD, pattern = "R|S|T|U|V|W") ~ "Societal Benefit",
    str_starts(NTEE_CD, pattern = "X") ~ "Religious",
    TRUE ~ "NA")) # this line is redundant as this would happen automatically - but everything else will be NA
```


Also for the quantile data:
```{r}
df_simplified_no_zero <-df_simplified_no_zero %>%
  mutate(NTEE_text = case_when(
    str_starts(NTEE_CD, pattern = "A")~ "Arts", # if NTEE_CD starts with A make new variable value "Arts" etc.
    str_starts(NTEE_CD, pattern = "B") ~ "Education",
    str_starts(NTEE_CD, pattern = "C|D") ~ "Enviornment/Animals", # if NTEE_CD value starts with C or D make new variable value "Environment/Animals"
    str_starts(NTEE_CD, pattern = "E|F|G|H") ~ "Health",
    str_starts(NTEE_CD, pattern = "I|J|K|L|M|N|O|P") ~ "Human Services",
    str_starts(NTEE_CD, pattern = "Q") ~ "International Affairs",
    str_starts(NTEE_CD, pattern = "R|S|T|U|V|W") ~ "Societal Benefit",
    str_starts(NTEE_CD, pattern = "X") ~ "Religous",
    TRUE ~ "NA")) # this line is redundant as this would happen automatically - but everything else will be NA
```


# Visualizations

## Deeper possible visualizations 

Overall log Asset amount figure:
```{r}
df_simplified_no_zero %>% 
ggplot(aes(y = ASSET_AMT_log, x = Percent_AA)) +
  geom_point() + geom_smooth(method = "loess")


```



## Quartile plots


Quartiles with log asset data:
```{r}
df_simplified_no_zero %>% 
ggplot(aes(y = ASSET_AMT_log, x = Percent_AA)) +
  geom_point() + facet_wrap(~ ASSET_quartile_text, scales = "free") +geom_smooth()
```






Look at log asset data for each NTEE type- **remember the caveat that there are many organizations that are not included because of NA or zero value ASSET_AMT**. However, still we can see that there is a trend towards lower amount of assets for most categories even with this limited data.

```{r}
df_simplified_no_zero %>%
  ggplot(aes(y = ASSET_AMT_log, x = Neighborhood)) +
  geom_boxplot()+ geom_jitter(width = .08) + 
  facet_wrap(~ NTEE_text, scales = "free_y") + 
  geom_smooth(method = "lm", se=TRUE, aes(group=1))
```

Compare all organizations by neighborhood AA status for log asset data. *remember the caveat that there are many organizations that are not included because of NA or zero value ASSET_AMT*

```{r}
df_simplified_no_zero %>%
  ggplot(aes(y = ASSET_AMT_log, x = Neighborhood)) +
  geom_boxplot()+ geom_jitter(width = .08) + geom_smooth(method = "lm", se=TRUE, aes(group=1))
```

## Association Tests

```{r}

summary(glm(data = df_simplified_no_zero, ASSET_AMT ~Percent_AA)) # for every increase in percent AA of the neighborhood there was a 266,249$ decrease in asset amount of the nonprofits in the neighborhood
# there is a less than 5% risk of concluding that an association exists between asset amount a percent AA of neighborhood when there is no actual association.


hist(df_simplified_no_zero$ASSET_AMT_log)
summary(glm(data = df_simplified_no_zero, ASSET_AMT_log~Percent_AA)) # for every increase in percent AA of the neighborhood there was a 266,249$ decrease in asset amount of the nonprofits in the neighborhood


glm(data = df_simplified_no_zero, ASSET_AMT_log ~ Percent_AA) %>% plot(which = 1:3)

#nonparametric test - because the residiuals looked skewed in the above qqplot
cor.test(df_simplified_no_zero$ASSET_AMT, df_simplified_no_zero$Percent_AA, method = "spearman", exact = FALSE)

```

Look at quartiles with log asset data:
*remember the caveat that there are many organizations that are not included because of NA or zero value ASSET_AMT*

```{r}
df_simplified_no_zero %>%
  ggplot(aes(y = ASSET_AMT_log, x = Neighborhood)) +
  geom_boxplot()+ geom_jitter(width = .08) + geom_smooth(method = "lm", se=TRUE, aes(group=1)) + facet_wrap(~ASSET_quartile_text, scales = "free_y")

```



First create data to make visualization easier
*caveat for the data:  that there are many organizations that are not included because of NA or zero value ASSET_AMT*

```{r}
quartile_data <-df_simplified_no_zero %>% 
  group_by(ASSET_quartile_text, Neighborhood) %>% 
  count()
quartile_data
```

Create percentage variable for each quantile
```{r}
quartile_data <- quartile_data %>%
  group_by(ASSET_quartile_text) %>% 
  mutate(Percent  = round(n/sum(n)*100)) 
quartile_data
```

Visuals...of the above data:

```{r}

quart_plot <- quartile_data %>% 
  ggplot(aes(x= ASSET_quartile_text, y = Percent,  fill = Neighborhood)) + 
    geom_col(position = position_dodge(width = .9))+
     scale_y_continuous(labels = function(x) paste0(x, "%")) +
     ylim(0,100) +
    scale_fill_grey() +
    theme_linedraw() +
    geom_text(aes(label = paste0(Percent, "%")), position = position_dodge(width = .9), vjust = -.5) 


quart_plot + labs(x = "Quartile based on nonprofit asset amount", y = "Percentage of nonprofits in the asset quartile")

```

**this does NOT include all 4,082 organizations**


## Overall Percentage Plot

First let's get a count of each - **NOTE we are keeping zero values and NA as low asset**!
The NA neighborhood means there is only one neighborhood that did not fit the categories or have information. We can drop this neighborhood.
```{r}
df_simplified %>%
  count(ASSET_High_text, Neighborhood)

df_simplified <-df_simplified %>%
  drop_na(Neighborhood)

df_simplified %>%
  count(ASSET_High_text, Neighborhood)
```


```{r}
High_asset_data <-df_simplified %>% 
  group_by(ASSET_High_text, Neighborhood) %>% 
  count() 
High_asset_data
```

Create percentage variable for each category:
```{r}
High_asset_data <- High_asset_data %>%
  group_by(Neighborhood) %>% 
  mutate(Percent_AA_cat = round(n/sum(n)*100)) 
High_asset_data
```

Visuals...of the above data:

```{r}

High_asset_data %>% 
  ggplot(aes(x= Neighborhood, y = Percent_AA_cat,  fill = ASSET_High_text)) + 
    geom_col(position = position_dodge(width = .9))+
     scale_y_continuous(labels = function(x) paste0(x, "%")) +
     ylim(0,100) +
    geom_text(aes(label = paste0(Percent_AA_cat, "%")), position = position_dodge(width = .9), vjust = -.5) +
  ylab("Percent of Neighborhood Category") +
  theme_linedraw() +
  scale_fill_grey() +
  theme(legend.title = element_blank())
```
**this includes all 4,082 organizations**

## High vs non asset by category
First create data to make visualization easier

```{r}
High_asset_data <-df_simplified %>%
  group_by(ASSET_High_text, Neighborhood, NTEE_text) %>% 
  count()
High_asset_data

#Create percentage variable for each category
High_asset_data <- High_asset_data %>%
  group_by(NTEE_text) %>% 
  mutate(Percent_ntee_cat = round(n/sum(n)*100)) 
High_asset_data
```

Visuals...of the above data:

```{r, eval = FALSE}

High_asset_data %>% 
  ggplot(aes(x= Neighborhood, y = Percent_ntee_cat,  fill = ASSET_High_text)) + 
    geom_col(position = position_dodge(width = .9))+
     scale_y_continuous(labels = function(x) paste0(x, "%")) +
    ylim(0, 100) +
    geom_text(aes(label = paste0(Percent_ntee_cat, "%")), position = position_dodge(width = .9), vjust = -.5) + facet_wrap(~NTEE_text) +
  theme_linedraw() +
  scale_fill_grey() +
  theme(legend.title = element_blank()) +
  ylab("Percentage for each category")

```

**this includes all 4,082 organizations**

### Count plots

```{r}
library(forcats)
df_simplified %>% group_by(NTEE_text) %>%summarize(count = n()) 


df_simplified %>% 
  group_by(NTEE_text, Neighborhood) %>%
  summarize(count = n()) %>% 
  mutate(NTEE_text = as_factor(NTEE_text)) %>%
  ggplot(aes(x = fct_reorder(NTEE_text, count, min), y = count , fill = Neighborhood)) + 
  scale_fill_viridis_d() +
  geom_col(position =position_dodge(width = .9))  + 
  ylab ("Number of Organizations") +
  theme_linedraw() +
  theme(axis.text.x = element_text(angle = 60, vjust = .5),
        axis.title.x = element_blank()) +
  scale_fill_grey()


 
```


**this includes all 4,082 organizations**



```{r}

plot2 <- df_simplified %>% 
    mutate(NTEE_text = as_factor(NTEE_text),
         NTEE_text = forcats::fct_relevel(NTEE_text, "International Affairs", "Environment/Animals", "Arts", "Religious", "Health","Education", "Societal Benefit", "Human Services", "NA" )) %>%
  group_by(NTEE_text, Neighborhood, ASSET_High_text) %>%
  summarize(count = n()) %>% 
  ggplot(aes(x = NTEE_text, y = count , fill = Neighborhood)) + 
  geom_col(position =position_dodge(width = .9))  + 
  facet_grid(rows = vars(ASSET_High_text)) +
  ylab ("Number of Organizations") +
  theme_linedraw() +
  theme(axis.text.x = element_text(angle = 60, vjust = .5),
        axis.title.x = element_blank()) +
  scale_fill_grey()
  
plot2

```

**this includes all 4,082 organizations**

## Distribution of percent AA 


```{r}

# get the neighborhood values if no removing rows for nonprofits with NA or zero assets
df_simplified %>% 
 distinct(`neighborhood name`, Percent_AA)

# get the neighborhood values after removing rows for nonprofits with NA or zero assets
df_simplified_no_zero %>% 
 distinct(`neighborhood name`, Percent_AA)
```


```{r}

# get the neighborhood values if no removing rows for nonprofits with NA or zero assets
df_simplified %>% 
 distinct(`neighborhood name`, Percent_AA) %>% pull(Percent_AA) %>% hist()

# get the neighborhood values after removing rows for nonprofits with NA or zero assets
df_simplified_no_zero %>% 
 distinct(`neighborhood name`, Percent_AA) %>% pull(Percent_AA) %>% hist()

```


